MacLeish

### 2016-06-09 README.Rmd
updated DESCRIPTION and README
version bump and updated README with CRAN badge

[![Travis-CI Build Status](https://travis-ci.org/beanumber/macleish.svg?branch=master)](https://travis-ci.org/beanumber/macleish)

@@

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("beanumber/etl")
devtools::install_github("beanumber/macleish")
```

>>>>

[![Travis-CI Build Status](https://travis-ci.org/beanumber/macleish.svg?branch=master)](https://travis-ci.org/beanumber/macleish)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/macleish)](https://cran.r-project.org/package=macleish)

@@

```{r, eval=FALSE}
install.packages("macleish")
```
